\documentclass[conference,compsoc]{IEEEtran}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{array}
\usepackage{colortbl}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cite}
\usepackage{xurl}

\newcommand{\method}{\textsc{PurGuard}}
\newcommand{\purifier}{\mathcal{P}}
\newcommand{\encoder}{\mathcal{F}}

\definecolor{metricpink}{RGB}{248,206,204}
\definecolor{metricsim}{RGB}{226,239,218}
\definecolor{metricblue}{RGB}{217,225,242}
\definecolor{avggray}{RGB}{235,235,235}

\title{\method: Purification-Aware Voice Protection Against Diffusion-Based Removal Attacks}

\author{\IEEEauthorblockN{Anonymous Authors}}

\begin{document}
\maketitle

\input{sections/abstract}

\begin{IEEEkeywords}
voice cloning, protective perturbations, diffusion purification, adversarial robustness, speaker identity
\end{IEEEkeywords}

\input{sections/introduction}
\input{sections/related_work}
\input{sections/methodology}
\input{sections/experiments}

\section{Limitations}
\label{sec:limitations}
\method{} currently studies surrogate-based purification-aware optimization and evaluates whether the resulting protection transfers to black-box target purifiers. 
This captures the practical case where the defender can train against a local purifier but does not know the attacker's deployed purifier; it does not fully cover no-surrogate defenders, learned purifier ensembles, or attackers who jointly adapt purification and synthesis. 
The current implementation also focuses on waveform-domain perturbations with bounded amplitude; future work should add psychoacoustic masking, over-the-air transformations, and human listening studies. 
We do not adversarially train a new purifier on \method-generated samples; the current held-out purifier, seed, backend, and verifier transfer tests are a bounded proxy for adaptive attackers, not a full solution to iterative attack-defense retraining.
We plan to extend the benchmark with broader stochastic purification trials before drawing claims across all purifiers and cloning backends.

\input{sections/conclusion}

\section{Ethical Considerations}
This work studies defenses against unauthorized voice cloning and therefore involves dual-use capabilities. The intended use of \method{} is to help speakers publish audio with reduced risk of impersonation after purification-based removal attacks. 
The evaluation uses CMU-ARCTIC, a public speech corpus, and reports aggregate metrics rather than speaker-identifying examples. 
Released artifacts will exclude cloned outputs that could be reused for impersonation or provide them only through controlled review channels with clear use restrictions. 
We do not claim that perturbation-based protection replaces policy, watermarking, authentication, or platform-side abuse detection; 
rather, it provides a data-source defense that can be combined with these safeguards.

\section{LLM Usage Statement}
Large language models were used as writing assistants for organization, editing, and wording suggestions. 
All technical claims, citations, experiments, and final text remain the responsibility of the authors.

\bibliographystyle{IEEEtran}
\bibliography{custom}

\end{document}
