\section{Conclusion}
\label{sec:conclusion}

\method{} reframes voice anti-cloning as a purification-aware protection problem. 
Instead of assuming that a protected waveform is fed directly into a cloning system, we model the stronger and increasingly realistic attacker who first removes perturbations with a purification front end. 
For diffusion purifiers, protection must survive not only direct speaker extraction but also the attacker's reverse denoising path; for traditional signal-processing front ends, it must also survive lightweight transformations such as resampling, quantization, filtering, and denoising.

\method{} addresses this gap by combining post-purification speaker disruption with trajectory-level deviation inside the purifier, and by providing a benchmark protocol with clean-purification controls and calibrated evaluator thresholds. 
Our analysis shows that trajectory supervision is a necessary complement to identity-only optimization: output-level gradients alone are insufficient when the purifier's stochastic path can route around the perturbation.

Several directions remain open. 
First, the current framework uses a differentiable surrogate purifier during optimization and evaluates transfer to black-box target purifiers; extending beyond this to no-surrogate or stronger ensemble-purifier settings is an important practical step. 
Second, psychoacoustic masking and over-the-air robustness constraints should be incorporated to tighten the perceptual budget. Third, the arms race between purification and protection is ongoing: as bridge-diffusion purifiers such as VocalBridge become stronger, protection methods will need to track the evolving attack surface. 
We release our implementation and evaluation protocol to support reproducible progress on this problem.
